Neural Models for Target-Based Computer-Assisted Musical Orchestration: A Preliminary Study

### 2021-06-24 csmc_mume_2020/paper/JCMS_2021/paper.tex
Clarify descr of picking random samples in sec 2.2

For a given number of instruments $N$, each input to our model is a combination of $N$ TinySOL samples chosen among an orchestra of 10 instruments. The data is generated by selecting $N$ random TinySOL samples, leading to a variety of instruments, pitches, and dynamics; we did not allow the same instrument to be chosen more than three times in order to ensure variety in the mixtures. Then the chosen samples are combined to be played simultaneously and normalized by the number of instruments. The resulting combination has a sample rate of $44100$Hz and is padded or trimmed to be exactly 4 seconds long.

>>>>

For a given number of instruments $N$, each input to our model is a combination of $N$ randomly selected TinySOL samples chosen from an orchestra of 10 instruments. The only constraint imposed on the random selection is that there cannot be more than 3 samples from the same instrument in any one combination. We do this to ensure instrumental variety in the combinations. By randomly selecting the samples, we achieve a variety of instruments, pitches, and dynamics while avoiding introducing any bias in the combinations that could result from hand-picking the samples. The selected samples are combined to be played simultaneously and the magnitude is normalized by the number of instruments. The resulting combination has a sample rate of $44100$Hz and is padded or trimmed to be exactly 4 seconds long.
